Commutative Character Sheaves

### 2015-11-11 followup.tex
Section 3 is working, but I've run out of steam for the day. More tomorrow.

\subsection{Commutative character sheaves on commutative groups}

@@

Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma_\beta : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows...

\begin{definition}\label{def:CCS}
The category $\CCS(G)$ of commutative character sheaves on $G$ is the full subcategory of $\CS'(G)$ consisting of triples $(\cs{L},\mu,\beta)$ such that the following diagram of Weil sheaves on $G \times G$ commutes.
  \[
  \begin{tikzcd}[row sep=30]
   m^*\cs{L} \arrow{d}{\gamma_\beta} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L})
  \end{tikzcd}
  \]
\end{definition}

We will see that, when $\beta$ exists for $(\cs{L},\mu)\in \CS(G)$, it is essentially unique.

@@

Let $G$ be as above.
Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
Let $a : H \times G\to G$ be a group action compatible with the group structure on $G$ and write $p : H\times G \to G$ for projection. 
Consider the morphisms
\[
\begin{tikzcd}
H \times H \times G 
\arrow[shift left=4]{r}{b_1, b_2, b_3} 
\arrow{r}{}
\arrow[shift right=4]{r}{} 
& H \times G 
\arrow[shift left=2]{r}{a}
\arrow[shift right=2]{r}[swap]{p}
 & G 
\end{tikzcd}
\]
defined by $b_1(h_1,h_2,g) = (n(h_1,h_2),g)$,  $b_2(h_1,h_2,g) = (h_1,a(h_2,g))$ and $b_3(h_1,h_2,g) = (h_2,g)$.
Then, $a\circ b_1 = a\circ b_2$ and $a\circ b_3 = p\circ b_2$ and $p\circ b_1 = p\circ b_3$.
An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
\[
\nu : a^*\cs{L} \to p^*\cs{L}
\] 
of Weil local systems on $H\times G$ such that the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes,
\[
\begin{tikzcd}
\ &  \arrow{dl}[swap]{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}{p\circ b_2 = a\circ b_3} & \\
b_1^* a^*\, \mathcal{L} \arrow{dr}[swap]{b_1^*(\nu)} &&&&   \arrow{dl}{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L}, & 
\end{tikzcd}
\]
and $s^*(\nu) = \id_{\cs{L}}$.
In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations above; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
\iffalse
On stalks, this condition is ...
\[
\begin{tikzcd}
\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
\end{tikzcd}
\]
\fi
Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
\[
\begin{tikzcd}
\arrow{d}[swap]{\nu} a^*\cs{L} \arrow{r}{a^*(\alpha)} & a^*\cs{L}' \arrow{d}{\nu'} \\
p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
\end{tikzcd}
\]
commutes.
This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.

@@

Now suppose $q : G \to G'$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
\[
\begin{tikzcd}
H\times G
 \arrow[shift left=2]{r}{a}
  \arrow[shift right=2,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
G'
\end{tikzcd}
\]
Let $\cs{L}'$ be a linear character sheaf on $G'$.
Consider the functor
\[
q^* : \CS(G') \to \CS(G)
\]
given on objects by $(\cs{L}',\mu') \mapsto (q^*\cs{L}', (q\times q)^* \mu', \nu_{\cs{L}'})$; cf [Dictionary].
Then $q^*\cs{L}'$ is an $H$-equivariant linear character sheaf on $G$ when equipped with the canonical isomorphism
\[
\nu_{\cs{L}'} : a^* q^* \cs{L}' \mathop{\longrightarrow}\limits^{\iso} (q\circ a)^* \cs{L}' = (q\circ p)^*\cs{L}' \mathop{\longrightarrow}\limits^{\iso} p^* q^*\cs{L}.
\]
This simple observation shows that the functor $q^* : \CS(G') \to \CS(G)$  factors according to the following commuting diagram of functors
\[
\begin{tikzcd}
\CS(G) &\arrow{l}[swap]{q^*} 
\CS(G') \arrow{dl}{\text{`comparison'}}\\
\arrow{u}{\text{forget}} \CS_{H}(G). & 
\end{tikzcd}
\]

@@

\begin{proof}
. . . 
So the lemma reduces to the claim: the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence. 
To see this, observe first that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
Moreover, if $Y \to X$ is a flat surjective morphism of affine schemes over $\Fq$, then the comparison functor $\Loc(X) \to \Loc(Y\to X)$ is an equivalence, with $\Loc(Y\to X)$ defined as in [].
It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fppf topology.
(This is a small variation on the proof of the fact that quasicoherent sheaves form a stack on sheaves in the fppf topology.)
Since $q : G\to G'$ is an $H$-torsor in the fppf topology, is now follows from descent theory that the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence.
\end{proof}

@@

We now suppose that $H$ is a subgroup of $G$ and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
Then we have the diagram
\[
\begin{tikzcd}
\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
G & & G \\
& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
\end{tikzcd}
\]
where $f(h,g) = (a(h,g) g^{-1}, g) = (h,g)$.
%Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq (i\circ p_1)$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
Then every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
\[
\beta : \cs{L}\vert_H \to (\EE)_{H}
\]
by 
\[
\nu = (\beta \boxtimes \id_{\cs{L}}) \circ  f^*\mu,
\] 
or more precisely, by the following diagram of isomorphisms.
\[
\begin{tikzcd}
a^*\cs{L} \arrow{d}{m\circ f = a} \arrow{rrr}{\nu}
&&& p^*\cs{L}\\
f^* m^*\cs{L} \arrow{r}{f^*\mu} & 
f^*(\cs{L}\boxtimes \cs{L}) \arrow{r} & 
\cs{L}\vert_{H} \boxtimes \cs{L} \arrow{r}{\beta\boxtimes \id_{\cs{L}}} & 
(\EE)_{H} \boxtimes \cs{L} \arrow{u} 
\end{tikzcd}
\]
In this way we see we may replace $(\cs{L},\mu,\nu)$ with a triple, $(\cs{L},\mu,\beta)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
The isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is constrained by two properties, corresponding to the diagrams in Sections [] and [].

\begin{lemma}
$\CS_H(G)$ is equivalent to the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$, with morphisms $\alpha : (\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ defined by the condition
$\alpha : (\cs{L},\mu) \to (\cs{L}',\mu')$ is a morphism in $\CS(G)$ and $\beta = \beta' \circ \alpha\vert_{H}$.
\end{lemma}

@@

\begin{proof}[Proof of Proposition~\ref{prop:Gder_triv}]
The abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$
and the quotient $q : G \to G\ab$ is faithfully flat and a $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
Then
\[
\begin{tikzcd}
%{} & G\times G \arrow{d}{c} &&&\\
1 \arrow{r}{i} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
\end{tikzcd}
\]
gives
\[
\begin{tikzcd}
\CS(H) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
\CS(G/H) \arrow{dl}{\text{`comparison'}} \\
\arrow{u}{\text{forget}} \CS'(G) \arrow{r}{\beta \mapsto \nu_\beta} & \CS_{H}(G) \arrow{u}{\text{forget}}  & 
\end{tikzcd}
\]
%
It now follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
On the other hand, by Lemma~[], $\CS_{G\der}(G)\to \CS'(G)$, defined by $(\cs{L},\mu,\nu)\mapsto (\cs{L},\mu, \beta_\nu)$, is an equivalence.
Since the essential image of the forgetful functor $\CS'(G)\to \CS(G)$ is precisely the category of $(\cs{L},\mu)\in \CS(G)$ such that $\cs{L}\vert_H \iso (\EE)_H$, this completes the proof of 
Proposition~\ref{prop:Gder_triv}.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:Gab}] 
\[
\begin{tikzcd}
\CS'(G) &\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{l}{\text{`comparison'}} \\
\CCS(G) \arrow{u}{\text{forget}}  & \CCS(G\ab) \arrow{u} 
\end{tikzcd}
\]

\end{proof}

>>>>

\subsection{Commutative character sheaves on commutative groups}\label{ssec:comcom}

@@

Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows.
Let $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
Then $c$ is a smooth morphism of $\Fq$ schemes and $c = m \circ (m \times (i \circ m \circ \theta))$.
Thus, $\beta : \cs{L}\vert_{G/\der} \to (\EE)_{G\der}$ determines
\[
\begin{tikzcd}
m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \arrow{r} & c^* \cs{L}\vert_{G\der} \arrow{r} &  (\EE)_{G\times G} \arrow{r} & (\EE)_G\otimes (\EE)_G.
\end{tikzcd}
\]
Using the monadic structure of the category of Weil local systems on $G\times G$, this isomorphism, in turn, defines the isomorphism
\[
\begin{tikzcd}
m^*\cs{L} \arrow{r}  & (\theta^* m^* i^*\cs{L})^\vee.\end{tikzcd}
\] 
Since $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ canonically, and since $\cs{L}^\vee \iso i^*\cs{L}$, canonically, this defines the promised isomorphism
\[
\begin{tikzcd}
\gamma : m^*\cs{L} \arrow{r} & \theta^* m^* \cs{L}.
\end{tikzcd}
\]

\begin{definition}\label{def:CCS}
The category $\CCS(G)$ of commutative character sheaves on $G$ is the full subcategory of $\CS'(G)$ consisting of triples $(\cs{L},\mu,\beta)$ such that the following diagram of Weil sheaves on $G \times G$ commutes,
  \[
  \begin{tikzcd}[row sep=30]
   m^*\cs{L} \arrow{d}{\gamma} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L})
  \end{tikzcd}
  \]
where $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$, above.
\end{definition}

%We will see that, when $\beta$ exists for $(\cs{L},\mu)\in \CS(G)$, it is essentially unique.

@@

Let $G$ be as above.
Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
Let $a : H \times G\to G$ be a group action compatible with the group structure on $G$ and write $p : H\times G \to G$ for projection. 
Consider the morphisms
\[
\begin{tikzcd}
H \times H \times G 
\arrow[shift left=4]{r}{b_1, b_2, b_3} 
\arrow{r}{}
\arrow[shift right=4]{r}{} 
& H \times G 
\arrow[shift left=2]{r}{a}
\arrow[shift right=2]{r}[swap]{p}
 & G 
\end{tikzcd}
\]
defined by $b_1(h_1,h_2,g) = (n(h_1,h_2),g)$,  $b_2(h_1,h_2,g) = (h_1,a(h_2,g))$ and $b_3(h_1,h_2,g) = (h_2,g)$.
Then, $a\circ b_1 = a\circ b_2$ and $a\circ b_3 = p\circ b_2$ and $p\circ b_1 = p\circ b_3$.
An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
\[
\nu : a^*\cs{L} \to p^*\cs{L}
\] 
of Weil local systems on $H\times G$ such that the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes,
\[
\begin{tikzcd}
\ &  \arrow{dl}{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
b_1^* a^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L}, & 
\end{tikzcd}
\]
and $s^*(\nu) = \id_{\cs{L}}$.
In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations above; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
\iffalse
On stalks, this condition is ...
\[
\begin{tikzcd}
\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
\end{tikzcd}
\]
\fi
Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
\[
\begin{tikzcd}
\arrow{d}[swap]{\nu} a^*\cs{L} \arrow{r}{a^*(\alpha)} & a^*\cs{L}' \arrow{d}{\nu'} \\
p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
\end{tikzcd}
\]
commutes.
This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.

@@

Now suppose $q : G \to G'$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
\[
\begin{tikzcd}
H\times G
 \arrow[shift left=2]{r}{a}
  \arrow[shift right=2,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
G'
\end{tikzcd}
\]
Let $\cs{L}'$ be a linear character sheaf on $G'$.
Consider the functor
\[
q^* : \CS(G') \to \CS(G)
\]
given on objects by $(\cs{L}',\mu') \mapsto (q^*\cs{L}', (q\times q)^* \mu', \nu_{\cs{L}'})$; cf [Dictionary].
Then $q^*\cs{L}'$ is an $H$-equivariant linear character sheaf on $G$ when equipped with the canonical isomorphism
\[
\nu_{\cs{L}'} : a^* q^* \cs{L}' \mathop{\longrightarrow}\limits^{\iso} (q\circ a)^* \cs{L}' = (q\circ p)^*\cs{L}' \mathop{\longrightarrow}\limits^{\iso} p^* q^*\cs{L}.
\]
This simple observation shows that the functor $q^* : \CS(G') \to \CS(G)$  factors according to the following commuting diagram of functors
\[
\begin{tikzcd}
\CS(G) &\arrow{l}[swap]{q^*} 
\CS(G') \arrow{dl}{\text{comparison}}\\
\arrow{u}{\text{forget}} \CS_{H}(G). & 
\end{tikzcd}
\]

@@

\begin{proof}
. . . 
So the lemma reduces to the claim: the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence. 
To see this, observe first that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
Moreover, if $Y \to X$ is a flat surjective morphism of affine schemes over $\Fq$, then the comparison functor $\Loc(X) \to \Loc(Y\to X)$ is an equivalence, with $\Loc(Y\to X)$ defined as in [].
It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fppf topology.
(This is a small variation on the proof that quasicoherent sheaves form a stack on sheaves in the fppf topology.)
Since $q : G\to G'$ is an $H$-torsor in the fppf topology, is now follows from descent theory that the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence.
\end{proof}

@@

We now suppose that $i : H \hookrightarrow G$ is a closed subgroup and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
Then we have the diagram
\[
\begin{tikzcd}
\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
G & & G \\
& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
\end{tikzcd}
\]
where $f(h,g) = (i(h),g)$.
% (a(h,g) g^{-1}, g) = (h,g)$.
%Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq (i\circ p_1)$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
Then every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
\[
\beta : \cs{L}\vert_H \to (\EE)_{H}
\]
by 
\[
\nu = (\beta \boxtimes \id) \circ  f^*\mu,
\] 
or more precisely, by the following diagram of isomorphisms.
\[
\begin{tikzcd}
\ & a^*\cs{L} \arrow{dl}{m\circ f = a} \arrow{r}{\nu} & p^*\cs{L} & \\
f^* m^*\cs{L} \arrow{dr}{f^*\mu} &&& (\EE)_{H} \boxtimes \cs{L} \arrow{ul}{p= p_1} \\ 
& f^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_\circ f = i}[swap]{p_2\circ f = \id}  & 
\cs{L}\vert_{H} \boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id} & 
\end{tikzcd}
\]
In this way we see we may replace $(\cs{L},\mu,\nu)$ with a triple, $(\cs{L},\mu,\beta)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
The isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is constrained conditions from Sections [] and [].

\begin{lemma}
$\CS_H(G)$ is equivalent to the category $\CS'(G)$ of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$, with morphisms $\alpha : (\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ defined by the condition
$\alpha : (\cs{L},\mu) \to (\cs{L}',\mu')$ is a morphism in $\CS(G)$ and $\beta = \beta' \circ \alpha\vert_{H}$.
\end{lemma}

@@

\begin{proof}[Proof of Proposition~\ref{prop:Gder_triv}]
The abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
Now,
\[
\begin{tikzcd}
%{} & G\times G \arrow{d}{c} &&&\\
1 \arrow{r} & G\der \arrow{r}{i} & G \arrow{r}{q} & G\ab \arrow{r} & 1
\end{tikzcd}
\]
gives
\[
\begin{tikzcd}
\CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{dl}{\text{comparison}} \\
\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu} &  \CS_{G\der}(G) \arrow{u}{\text{forget}}  & 
\end{tikzcd}
\]
%
Since the quotient $q : G \to G\ab$ is a trivial $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}, 
it now follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
On the other hand, by Lemma~[], $\CS'(G) \to \CS_{G\der}(G)$, defined by $(\cs{L},\mu,\beta)\mapsto (\cs{L},\mu, \nu)$, is an equivalence.
Since the essential image of the forgetful functor $\CS'(G)\to \CS(G)$ is precisely the category of $(\cs{L},\mu)\in \CS(G)$ such that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$, this completes the proof of Proposition~\ref{prop:Gder_triv}.
%that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ if and only if $\cs{L} = q^*\cs{L}\ab$ for some $\cs{L}\ab \in \CS(G\ab)$.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:Gab}] 
By Definition~\ref{def:CCScom}, $\CCS(G\ab) \to \CS(G\ab)$ is a full subcategory.
Since the comparison functor $\CS(G\ab) \to \CS_{G\der}(G)$ is an equivalence, it determines a full subcategory $\CCS_{G\der}(G)$ which is equivalent to $\CCS(G\ab)$. 
\[
\begin{tikzcd}
\CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{dl}{} \\
\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu} &  \CS_{G\der}(G) \arrow{u}{\text{forget}}  & \CCS(G\ab) \arrow{u} \arrow{dl} \\
\CCS(G) \arrow{u} \arrow{r}{\beta \mapsto \nu} & \arrow{u}  \CCS_{G\der}(G) & 
\end{tikzcd}
\]
The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of the equivalence $\CS_{G\der}(G) \to \CS'(G)$ is $\CCS(G)$.
To that end, suppose $(\cs{L},\mu,\beta)\in \CS'(G)$ and $(\cs{L},\mu,\nu) = q^*(\cs{L}\ab,\mu\ab)$;
we must show that $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ in Section~\ref{ssec:comcom}.
This determines a rigidification $r : \cs{L}_1 \to \EE$ by ....\todo{I've sorted this out, but have also run out of steam for the day. I'll write it up tomorrow.}
\end{proof}
